---
title: "DDP - Week 3 assignment"
author: "Sergej Horvat"
date: '18 rujna 2017 '
output:
  ioslides_presentation: default
  slidy_presentation: default
---


## Instructions
Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity! 

## Plotly graph of reproducible resarch week 2 assignment

```{r, echo=FALSE , warning=FALSE, error=FALSE, results='hide', message=FALSE}
data <- unzip(zipfile = "activity.zip")
activity <- read.csv(data)
activity <- activity[complete.cases(activity),] 
activityAgg <- aggregate(activity$steps~activity$date, activity,sum)


library (plotly)
activityAgg$`activity$date`<-as.POSIXct(activityAgg$`activity$date`,"%e/%m/%y")

#as.POSIXct(strftime (as.Date(activityAgg$`activity$date`),format="%d-%m-%y"))
```

```{r, echo=FALSE , warning=FALSE, error=FALSE}
plot_ly(data=activityAgg,
  x=activityAgg$`activity$date`,
  y=activityAgg$`activity$steps`,
  type="scatter",
  mode="density"
)
```


## Thanks
